---
output:
  pdf_document: default
  html_document: default
---

title: "" author: "Vryan Feliciano" output: pdf_document: default html_document: default

# Loading and Packages

```{r}
library(tidyverse)
library(rmarkdown)
library(Hmisc)

load("../test_data_derived.Rdata") 
# Rdata is a file type that saves information/output from a script/markdown in R. This specific one loads an Rdata file that holds one dataframe called "test_data_derived".
```

# HL's DataFrame Cleaning, to Prep for Tasks
```{r}
# this is fixing hannahs dataframe mistake 
test_data_derived <- test_data_derived %>% 
  ungroup(gameID)

```

# Data Background

## Each row in this dataframe indicates participant's response on one item. In total, there are 66 items; not all participants might have answered the 66 items.

## The variables:

-   gameID: Each subject's unique identifying number
-   The sum of unique gameID is the sample size
-   version: Participants could have either take VLAT ---\> GGR (VLAT_GGR), or GGR ---\> VLAT (GGR_VLAT)
  -   version was recoded into numerical representations: VLAT_GGR == 1, GGR_VLAT == 2

# TASK 1: record the variable version to have numerical indicators instead of a string (use piping!!)
```{r}
# so we already have a dataframe, test_data_derived. we piped the "version" variable in the dataframe using the count() function to find how many unique cases of GGR_VLAT and VLAT_GGR. 
test_data_derived <- test_data_derived %>%
  mutate(version = recode(version, 'GGR_VLAT'=1, 'VLAT_GGR'=2))

# okay so for some reason "count(version)" doesn't work
# tally(version)

# base R recode(), this doesnt work but also tidyverse foreverrrr
# recoded_tdd <- recode(test_data_derived$version, "GGR_VLAT"=1, "VLAT_GGR"=2)
head(test_data_derived$version)
# NAs are possible, likely because... maybe respondents did not complete either?
```

# TASK 2: convert the variables vlat_time and ggr_time to minutes, creating new variables vlat_time_m & ggr_time_m (use piping!!)
```{r}
# so based on what me and HL talked about regarding using time to measure
# a person's response time or focus & based on my own mathmeatical reasoning:
# vlat_time and ggr_time are measured in MILLISECONDS, because typically that's how we measure rt
# so to get them into minutes, we need to convert to seconds first, then minutes
test_data_derived <- test_data_derived %>%
  mutate(vlat_time_m = ((vlat_time/1000)/60), 
         ggr_time_m = ((ggr_time/1000)/60))

head(test_data_derived$vlat_time_m)
head(test_data_derived$ggr_time_m)
```

# TASK 3: hardest one: create a new variable that is called rt_cv (coefficient of variation) which is calculated by: "for each subject: trial level reaction time standard deviation / trial level reaction time mean"
## HL Example
```{r}
# HL Example -- probs not accurate to what you're gonna see? YES, BECAUSE IT'S ONLY ONE SUBJECT
# the thing is, you're doing this for each subject
hl_list <- c(0.33,0.34,0.35,0.5,0.9)
hl_list

hl_cv <- sd(hl_list) / mean(hl_list)
hl_cv
```
## TASK SOLUTION:
```{r}
# for each subject... i would have to group by each unique gameID? so group_by() or unique()? filter()?
# what is trial level reaction time? is it "rt" or "rt_min variable -- probably just use rt
test_data_derived <- test_data_derived %>%
  group_by(gameID) %>%
  mutate(rt_cv = (sd(rt) / mean(rt)))

head(test_data_derived$rt_cv)
# yeah that looks right... but is it? :')
```
