---
title: "gcb_demographics_analysis"
author: "Vryan Feliciano"
date: "2022-11-07"
output: html_document
pdf_document: default
html_document: default
---

# Loading Packages, Dataset, and Global Variables
```{r}
# Load libraries:
suppressPackageStartupMessages({library(tidyverse)
                               library(rmarkdown)
                               library(Hmisc)
                               library(grid)
                               library(gridExtra)}) 

# Load dataset:
load("test_data_derived_vf.Rdata") 
load("survey_derived.Rdata")

# Source in scripts for functions:
## N/A

# Create global variables:
gcb_item_total <- length(unique(test_data_derived$gcbID))
```

# Does formal math education hone these skills of graph comprehension, insofar as these classes should help your understanding of certain skills?

# Merge the two datasets, so that piping can be easier
```{r}
# Merging these two dataframes will making piping easier, because
# I'll just be dealing with one merged dataframe and not two separate ones
test_data_joined <- merge(test_data_derived_vf, survey_derived)

```

# Create composite score of math history
```{r}
test_data_joined <- test_data_joined %>%
  group_by(gameID) %>% 
  mutate(math_composite = algebra + statistics + calculus)
```

# Create overall bar chart of math history vs. task accuracy
```{r}
math_accuracy_graph <- ggplot(data=test_data_joined, 
                              aes(x=math_composite, y=accuracy_within_task_vf)) +
  stat_summary(fun="mean", geom="bar") +
  stat_summary(fun.data="mean_cl_boot", geom="errorbar", size=0.2, width=0.25) +
  coord_cartesian(ylim=c(0,1)) +
  labs(title="How well are people doing on these tasks \n based on their math history?",
       x="Math Composite Score", y="Accuracy \n (Percent Correct)")

math_accuracy_graph
```

# Are there any difference between math background and how well people do?
## Create sub-viz of statistics/no statistics
```{r}
stat_accuracy_graph <- ggplot(data=test_data_joined,
                                   aes(x=as.factor(statistics), y=accuracy_within_task_vf)) +
  stat_summary(fun="mean", geom="bar") +
  stat_summary(fun.data="mean_cl_boot", geom="errorbar", size=0.2, width=0.25)  +
  coord_cartesian(ylim=c(0,1)) +
  scale_x_discrete(labels=c("no statistics", "has statistics")) +
  labs(x="Statistics Background", y="Accuracy \n (Percent Correct)")

stat_accuracy_graph
```
## Create sub-viz of calculus/no calculus
```{r}
calc_accuracy_graph <- ggplot(data=test_data_joined,
                                   aes(x=as.factor(calculus), y=accuracy_within_task_vf)) +
  stat_summary(fun="mean", geom="bar") +
  stat_summary(fun.data="mean_cl_boot", geom="errorbar", size=0.2, width=0.25)  +
  coord_cartesian(ylim=c(0,1)) +
  scale_x_discrete(labels=c("no calculus", "has calculus")) +
  labs(x="Calculus Background", y="Accuracy \n (Percent Correct)")

calc_accuracy_graph
```
## Create sub-viz of calculus/no calculus
```{r}
alge_accuracy_graph <- ggplot(data=test_data_joined,
                                   aes(x=as.factor(algebra), y=accuracy_within_task_vf)) +
  stat_summary(fun="mean", geom="bar") +
  stat_summary(fun.data="mean_cl_boot", geom="errorbar", size=0.2, width=0.25) + 
  coord_cartesian(ylim=c(0,1)) +
  scale_x_discrete(labels=c("no algebra", "has algebra")) +
  labs(x="Algebra Background", y="Accuracy \n (Percent Correct)")

alge_accuracy_graph
```
## Combined background graph using grid.arrange()
```{r}
combined_accuracy_graph <- grid.arrange(stat_accuracy_graph, calc_accuracy_graph, alge_accuracy_graph, 
                                        nrow=1, top=textGrob("Are there any differences between math backgrounds and how well people do?")) +
  theme_bw()

combined_accuracy_graph

```

