---
  output:
  pdf_document: default
html_document: default
---
  
  title: "" author: "Vryan Feliciano" output: pdf_document: default html_document: default

# Loading Packages, Dataset, and Global Variables
```{r}
# Load libraries:
suppressPackageStartupMessages({library(tidyverse)
                               library(rmarkdown)
                               library(Hmisc)}) 

# Load dataset:
load("../test_data_derived.Rdata") 

# Source in scripts for functions:
source("mode.R")

# Create global variables:
gcb_item_total <- length(unique(test_data_derived$gcbID))#test_data_derived%>%distinct(gcbID)%>%count()
```

# 2: Load the dataset, and save if with affix _vf
```{r}
# using subset() to subset out variables that I have to replicate
# and save that subsetted dataset as my own, test_data_derived_vf
test_data_derived_vf <- test_data_derived %>%
  subset(select=-c(percent_correct_total, percent_correct_total_sd, 
                   vlat_percent, ggr_percent, accuracy_within_task, 
                   accuracy_within_graph, match_within_task,
                   match_between_task, match_within_graph,
                   match_between_graph,items_answered))
```

# Task 3:
## Calculate percent correct for each participant, store this as a new variable
```{r}
# group_by() participant's unique ID (gameID), and then for each participant calculate the percent correct, where: 
# percent correct = sum what a participant got correct / the total number of GCB items, 66
test_data_derived_vf <- test_data_derived_vf %>%
  group_by(gameID) %>%
  mutate(percent_correct_total_vf=sum(accuracy) / gcb_item_total) # fix later
```

# Task 3
## Calculate the percent correct for just VLAT items and just GGR items for each participant, store this value as a new variable for each participant
```{r}
# The following code gets both,
test_data_derived_vf <- test_data_derived_vf %>%
  group_by(origStudy, subID) %>%
  mutate(vlat_ggr_percent_vf = mean(accuracy))

# I still want individual variables for vlat and ggr...
```

# Task 4
## Calculate the percent correct for both origStudy_taskCategorization and graphType, store this as a value for each participant
```{r}
#
test_data_derived_vf <- test_data_derived_vf %>%
  group_by(origStudy_taskCategorization, subID) %>% 
  mutate(accuracy_within_task_vf = mean(accuracy))

test_data_derived_vf <- test_data_derived_vf %>%
  group_by(graphType, subID) %>% 
  mutate(accuracy_within_graph_vf = mean(accuracy))
```

# Task 5
## Match within origStudy_taskCategorization & within graphType using Modal Percentage
## Modal Percentage for within tasks:
```{r}
# Modal Percentage is calculated
test_data_derived_vf <- test_data_derived_vf %>%
  group_by(origStudy_taskCategorization) %>%
  mutate(task_modalp_correct_vf = mode(accuracy_within_task_vf),
         task_modalp_incorrect_vf = mode(1 - accuracy_within_task_vf),
         task_modalp_vf = ifelse(task_modalp_correct > task_modalp_incorrect, task_modalp_correct,
                              ifelse(task_modalp_incorrect > task_modalp_correct, task_modalp_incorrect, 
                                     ifelse(task_modalp_correct == task_modalp_incorrect, task_modalp_correct, 0))))
```

## Modal Percentage for within graphType:
```{r}
# why aren't you working
test_data_derived_vf <- test_data_derived_vf %>%
  group_by(graphType) %>%
  mutate(graph_modalp_correct_vf = mode(accuracy_within_graph_vf),
         graph_modalp_incorrect_Vf = mode(1 - accuracy_within_graph_vf),
         graph_modalp_vf = ifelse(graph_modalp_correct > graph_modalp_incorrect, graph_modalp_correct,
                              ifelse(graph_modalp_incorrect > graph_modalp_correct, graph_modalp_incorrect, 
                                     ifelse(graph_modalp_correct == graph_modalp_incorrect, graph_modalp_correct, 0))))
```
