---
title: "viz_creating"
author: "Vryan Feliciano"
date: "2022-11-06"
output: html_document
pdf_document: default
html_document: default
---

# Loading Packages, Dataset, and Global Variables
```{r}
# Load libraries:
suppressPackageStartupMessages({library(tidyverse)
                               library(rmarkdown)
                               library(Hmisc)}) 

# Load dataset:
load("test_data_derived_vf.Rdata") 

# Source in scripts for functions:
## N/A

# Create global variables:
## to replicate HL's viz, we order x-labels for task type in a similar order
## this does not need to be done for graph type
task_graph_order <- c('level_1', 'level_2', 'level_3',
                      'retrieve_value', 'find_extremum', 'find_anomolies',
                      'make_comparisons', 'determine_Range', 'characterize_distribution',
                      'find_correlations_trends', 'find_clusters')

```

# Creating Bar Chart Viz: taskType vs. accuracy; "How well are people doing on these tests and which types of questions seem to be the most difficult?"
```{r}
task_accuracy_graph <- ggplot(data=test_data_derived_vf, aes(x=factor(origStudy_taskCategorization, task_graph_order), y=accuracy_within_task_vf,
                                                       fill=test_data_derived_vf$origStudy)) +
  stat_summary(fun="mean", geom="bar") +
  stat_summary(fun.data="mean_cl_boot", geom="errorbar", size=0.2, width=0.25) +
  scale_x_discrete(labels=c('read data \n level 1', 'read between data \n level 2', 'read beyond data \n level 3',
                            'retrieve \n value', 'find \n extremum', 'find \n anomolies',
                            'make \n comparisons', 'determine \n range', 'characterize \n distribution',
                            'find \n trends/correlations', 'find \n clusters'), 
                   guide=guide_axis(angle=70, n.dodge=1)) +
  coord_cartesian(ylim=c(0,1)) +
  labs(x="Question Type", y="Accuracy \n (Percent Correct)", fill="Original Study") +
  theme_bw()

task_accuracy_graph
```

# Creating Bar Chart Viz: taskType vs. matched scores (modal percentage)
```{r}
task_modalp_graph <- ggplot(data=test_data_derived_vf, aes(x=factor(origStudy_taskCategorization, task_graph_order), y=task_modalp_vf,
                                                       fill=test_data_derived_vf$origStudy)) +
  stat_summary(fun.y=mean, geom="bar", alpha=0.7) +
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.5) +
  scale_x_discrete(labels=c('read data \n level 1', 'read between data \n level 2', 'read beyond data \n level 3',
                            'retrieve \n value', 'find \n extremum', 'find \n anomolies',
                            'make \n comparisons', 'determine \n range', 'characterize \n distribution',
                            'find \n trends/correlations', 'find \n clusters'), 
                   guide=guide_axis(angle=70, n.dodge=1)) +
  coord_cartesian(ylim=c(0.5,1)) +
  labs(x="Question Type", y="Inter-Item Reliability \n (Modal Percentage)", fill="Original Study") +
  theme_bw()

task_modalp_graph
```
# Creating Bar Chart Viz: INCORRECT taskType vs. matched scores (modal percentage)
```{r}
incorrect_task_modalp_graph <- ggplot(data=test_data_derived_vf, aes(x=factor(origStudy_taskCategorization, task_graph_order), y=incorrect_task_modalp_vf,
                                                       fill=test_data_derived_vf$origStudy)) +
  stat_summary(fun.y=mean, geom="bar", alpha=0.7) +
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.5) +
  scale_x_discrete(labels=c('read data \n level 1', 'read between data \n level 2', 'read beyond data \n level 3',
                            'retrieve \n value', 'find \n extremum', 'find \n anomolies',
                            'make \n comparisons', 'determine \n range', 'characterize \n distribution',
                            'find \n trends/correlations', 'find \n clusters'), 
                   guide=guide_axis(angle=70, n.dodge=1)) +
  coord_cartesian(ylim=c(0.5,1)) +
  labs(x="Question Type", y="Inter-Item Reliability \n (Modal Percentage)", fill="Original Study") +
  theme_bw()

incorrect_task_modalp_graph
```

# Creating Bar Chart Viz: graphType vs. accuracy
```{r}
graph_accuracy_graph <- ggplot(data=test_data_derived_vf, aes(x=graphType, y=accuracy_within_graph_vf)) +
  stat_summary(fun="mean", geom="bar") +
  stat_summary(fun.data="mean_cl_boot", geom="errorbar", size=0.2, width=0.25) +
  scale_x_discrete(labels=c('area chart', 'bar chart', 'bubble chart', 'choropleth map', 'histogram', 'icon array',
                            'line chart', 'normalized stacked \n bar chart', 'pie chart', 'scatterplot',
                            'stacked area chart', 'stacked bar chart', 'tree map'), 
                   guide=guide_axis(angle=70, n.dodge=1)) +
  coord_cartesian(ylim=c(0,1)) +
  labs(x="Graph Type", y="Accuracy \n (Percent Correct)") +
  theme_bw()

graph_accuracy_graph
```

# Creating Bar Chart Viz: graphType vs. matched scores (modal percentage)
```{r}
graph_modalp_graph <- ggplot(data=test_data_derived_vf, aes(x=graphType, y=graph_modalp_vf)) +
  stat_summary(fun="mean", geom="bar") +
  stat_summary(fun.data="mean_cl_boot", geom="errorbar", size=0.2, width=0.25) +
  scale_x_discrete(labels=c('area chart', 'bar chart', 'bubble chart', 'choropleth map', 'histogram', 'icon array',
                            'line chart', 'normalized stacked \n bar chart', 'pie chart', 'scatterplot',
                            'stacked area chart', 'stacked bar chart', 'tree map'), 
                   guide=guide_axis(angle=70, n.dodge=1)) +
  coord_cartesian(ylim=c(0.5,1)) +
  labs(x="Graph Type", y="Inter-Item Reliability \n (Modal Percentage)") +
  theme_bw()

graph_modalp_graph
```